\section{Exercises}
\label{exercisesChapterProbability}
\begin{problem} %(From \cite{Kim}) %Exercise 22
  Let $E_1$ be the events that a horse will have 
  strongyles parasites and $E_2$ a horse will have
  piroplasmosis. Suppose $\Pr (E_1) = 0.34$ and $\Pr (E_2) = 0.54$. If
  $\Pr (E_1\cap E_2) = 0.25$, what is the chance of a horse will have
  at least one of these diseases?
\end{problem}


\begin{problem} %(From \cite{Kim}) %Exercise 25
  A team of vet professionals visited farms in the Southwest. Among
  the samples of 568 farms they visited, 28 of them had at least two
  animals with botulism. What is the estimated probability that a
  farm from this area has at most one animal with botulism?
\end{problem}
\begin{problem} %(From \cite{Kim}) %Exercise 15
  Let $B$ be the event that at least one  rabbit in a farm with 200 rabbits as having
  buphthalmia, and $D$ be the event that the diet in the farm has a
 Vitamin A deficit.	Let
  $\Pr ( B)	= 0.15$	and	$\Pr( D )	=	0.24$.	If
  $B$	and	$D$	are	statistically independent, what is the
  $\Pr (B \cup D)$?
\end{problem}


\begin{problem} %(From \cite{Kim})
Suppose that $A$ is the event of a mother rabbit having  a splay leg
and that $B$ is the event of a father having a splay leg. If it is known that $\Pr (A) = 0.10$, $\Pr (B) = 0.20$, and $\Pr ( A\cap B ) = 0.02$, are the events $A$ and $B$ statistically independent?
\end{problem}

\begin{problem}
   If $Z$ is a standard normal random variable, find each of the
following probabilities: 
\begin{multicols}{3} 
  \begin{enumerate}\renewcommand{\theenumi}{\roman{enumi}}
  \item $\Pr(0<Z<1.5)$ 
   \item $\Pr(0.39<Z<2.67)$
   \item $\Pr(Z>-2.24)$
   \item $\Pr(Z>0.02)$
   \item $\Pr(|Z| > 1)$
   \item $\Pr(-1.23<Z<-0.3)$
   \item $\Pr(|Z|>2)$
   \item $\Pr(-0.4<Z<1.5)$
   \end{enumerate}
   \end{multicols}
\end{problem}

\begin{problem}
  Assume that $Z$ is a standard normal variable.  Find $z_0$ such that
  the following statement is true.
  \begin{multicols}{2}
    \begin{enumerate} \renewcommand{\theenumi}{\roman{enumi}}
    \item  $\Pr(Z<z_0)=0.6368307$ % 0.35
   \item $\Pr(Z<z_0)=0.9382198$ % 1.54
   \item $\Pr(0<Z<z_0)= 0.4846137$  %2.16
   \item $\Pr(z_0<Z)=0.8925123$ %-1.24
    \end{enumerate}
  \end{multicols}
\end{problem}

\begin{problem}
  If $X$ is normally distributed variable with $\mu=16$ and $\sigma=4$, find
  each of the following probabilities: 
  \begin{multicols}{3}
    \begin{enumerate} \renewcommand{\theenumi}{\roman{enumi}}
    \item $\Pr(X<27)$ 
    \item $\Pr(X<10)$ 
    \item $\Pr(10.8<X<12.4)$
    \end{enumerate}
  \end{multicols}
\end{problem}

\begin{problem} 
  The historical data indicate that the scores of the National Board
  Exam Part I taken during the second year in vet school are
  normally distributed with the mean score of 73.1 and the variance of
  16.2. In order to pass the exam one must score at least 75. Compute
  the percent of students that is expected to pass  this year's exam.

\end{problem}
\begin{problem}%(From \cite{Hauessler})
  The scores on a national achievement test are normally distributed
  with mean 500 and standard deviation 100. What percentage of those
  who took the test had a score between 300 and 700?
\footfullcite{haeussler2006introductory}
\end{problem}


\begin{problem}  %(From \cite{Hauessler})
  In a test given to a large group of peoples the score were normally
  distributed with mean 65 and standard deviation 10. What is the
  least whole--number score that a person could get and yet score in
  about the top 20\%? \footnote{Ibidem}
\end{problem}

\begin{problem}  %(From \cite{Hauessler})
  The heights (in inches) of adults in a large population are normally
  distributed with $\mu=68$ and $\sigma=3$. What percentage of the
  group is under 6 feet tall? \footnote{Ibidem}
\end{problem}

\begin{problem} %(From \cite{Hauessler})
  The IQs of a large population of children are normally distributed
  with mean 100.4 and standard deviation 11.6. 
  \begin{enumerate} \renewcommand{\theenumi}{\roman{enumi}}
  \item What percentage of the children have IQs greater that 125? 
  \item About 90\% of the children have IQs greater than what value? \footnote{Ibidem}
  \end{enumerate}
\end{problem}


\begin{problem}
  The weight of a one-year-old gorilla is approximately normal
  distributed with mean $\mu=7$\,kg and standard deviation
  $\sigma=2$\,kg. 
  \begin{enumerate} \renewcommand{\theenumi}{\roman{enumi}}
  \item Calculate an interval whose midpoint is the mean and that
    contains 95\% of the weights of one-year-old gorillas. 
 \item Calculate an interval  whose midpoint is the mean and that
    contains 98\% of the weights of one-year-old gorillas. 
 \item Calculate an interval  that
    contains 95\% of the weights of the heaviest one-year-old
    gorillas. 
 \item What is the percentage of one-year-old gorillas whose weight is less than
   3.5\,kg?
 \item What  is the percentage of one-year-old gorillas whose weight is greater than
   4.5\,kg?
  \item What  is the percentage of one-year-old gorillas whose weight is between 6
    and 8\,kg?
\item What  is the percentage of one-year-old gorillas whose weight is between 4 
    and 5\,kg?
\item What is the percentile of one-year-old gorilla that weights
  10.5\,kg? 
  \end{enumerate}
\end{problem}

\begin{problem}
  The height  of an adult Appaloosa horse is approximately normal
  distributed with mean $\mu=150$\,cm and standard deviation
  $\sigma=12$\,cm.
  \begin{enumerate} \renewcommand{\theenumi}{\roman{enumi}}
  \item Calculate an interval whose midpoint is the mean and that
    contains 95\% of the heights of adult  Appaloosa horses. 
 \item Calculate an interval  whose central point is the mean and that
    contains 90\% of the heights of adult  Appaloosa horses. 
 \item Calculate an interval  that
    contains 95\% of the heights of the shortest adult  Appalosa horses. 
 \item What is the percentage of adult  Appaloosa horses whose height is less than
   158\,cm?
 \item What  is the percentage of adult  Appaloosa horses with height is greater than
   141\,cm?
  \item What  is the percentage of adult  Appaloosa horses with height between 140
    and 170\,cm?
\item What is the percentile of adult  Appaloosa horses that is 
  175\,cm? 
  \end{enumerate}
\end{problem}