\section{Exercises}
\label{ch5Exercises}
% \begin{problem} %(From \cite{Kim}) % Example 8.4.3 Known variance
%   Homocysteine is a by--product of protein processing. It is as much
%   an artery--clogging
% villain as cholesterol is in contributing to heart attacks and
% strokes. A study was conducted to investigate if there exists any
% difference in homocysteine levels between adult males living in the
% Southwest and those in the Midwest. Suppose past medical data
% indicated that the level of homocysteine of those living in the
% Southwest is normally distributed with mean $14\,\textrm{mg/dL}$ and
% standard deviation $3.26\,\textrm{mg/dL}$. Assume that the distribution of the homocysteine levels of midwestern counterparts is also normal, with the same known standard deviation, $\sigma= 3.26\,\textrm{mg/dL}$. Investigators randomly selected 15 individuals from the Midwest, and their homocysteine levels were measured. If the sample
% mean of the 15 observations was $\overline{x}= 13\,\textrm{mg/dL}$, what conclusions can be drawn from this evidence? Compute the $p$--value of the test.\\
% Note that the significance level $\alpha= 0.05$.\footfullcite{kim2008biostatistics}
% \end{problem}


\begin{problem}  %  (From \cite{Kim}) % Example 8.5.1
  Although obstructive sleep apnea (OSA) patients tend to be obese, a
  significant number of them are not. A recent study suggested that
  fat deposition around the neck may be a factor associated with OSA
  in non--obese patients. Suppose that apnea hypopnea index (AHI), an
  index used to quantify the degree of obstructive sleep apnea, is
  normally distributed and that the average AHI for non--obese
  patients, whose body mass index is less than 25, is 7.65. It has
  been Dr. Johnston’s experience that AHI for obese patients
  (say, $\textrm{BMI} > 35$) is not much different from that of the non--obese. To validate his assertion Dr. Johnston took a sample of 15 obese patients and
measured their AHI. The sample 	mean~($\overline{x}$)	and	variance~($s^2$) of his measurements are 9.77 and 11.14, respectively. State the hypotheses and perform a test at the significance level $\alpha= 0.05$.\footnote{ibidem}
\end{problem}

\begin{problem}  % (From \cite{Kim}) % Example 8.5.2
  Coronary heart disease is the leading cause of morbidity and
  mortality throughout the world. A research goup  investigated the
  possible association between periodontal health and coronary heart
  disease in patients with acute myocardial infarction (AMI) and
  chronic coronary heart disease (CCHD). Based on the physical
  examination done prior to admission into a clinical trial, it was
  determined that the average level of triglycerides for the patients
  with AMI is $196.49
\,\textrm{mg/dl}$. Suppose the investigators claimed that the
triglyceride level for the patients with the CCHD should be lower than
that value for the patients in the AMI group. To confirm their claim, the investigators randomly selected 27 patients with CCHD and observed their triglyceride levels. The data
yielded $\overline{x}= 155.23\,\textrm{mg/dl}$ and $s = 88.04\,\textrm{mg/dl}$. Assume that the triglyceride levels are normally distributed. How would you state the hypotheses for the investigators, and what could you conclude? \footnote{ibidem}
\end{problem}

\begin{problem} 
  Body mass index is calculated by dividing a person's weight by the square of his or her height; it is a measure of the extent to which the individual is overweight. For the population of middle-aged men who later develop diabetes mellitus, the distribution of baseline body mass indices is approximately normal with an unknown mean $\mu$ and standard deviation $\sigma$. A sample of 58 men selected from this group has mean $\overline{x}=25.0\,\textrm{kg/m}^2$ and standard deviation $s=2.7\,\textrm{kg/m}^2$.
  \begin{enumerate}
  \item Construct a 95\% confidence interval for the population mean $\mu$.
  \item At the 0.05 level of significance, test whether the mean baseline body mass index for the population of middle--aged men who do develop diabetes is equal to $24.0\,\textrm{kg/m}^2$, the mean for the population of men who do not. What is the $p$--value of the test?
  \item What do you conclude?
  \item Based on the 95\% confidence interval, would you have expected to reject or not to reject the null hypothesis? Why?
\end{enumerate}
\end{problem}

\begin{problem} 
  The population of male industrial workers in London who have never experienced a major coronary event has mean systolic blood pressure 136\,mmHg and mean diastolic blood pressure 84\,mmHg. You might be interested in determining whether these values are the same as those for the population of industrial workers who have suffered a coronary event.
  \begin{enumerate}
  \item A sample of 86 workers who have experienced a major coronary event has mean systolic blood pressure $\overline{x}$=143\,mmHg and standard deviation $s$=24.4\,mmHg. Test the null hypothesis that the mean systolic blood pressure for the population of industrial workers who have experienced such an event is identical to the mean for the workers who have not, using a two--sided test at the $\alpha$=0.10 level.
  \item The same sample of men has mean diastolic blood pressure
    $\overline{x}$=87\,mmHg and standard deviation $s$=16.0\,mmHg. Test the null hypothesis that the mean systolic blood pressure for the population of workers who have experienced a major coronary event is identical to the mean for the workers who have not.
  \item How do the two groups of workers compare?
\end{enumerate}
\end{problem}




\begin{problem}   % (From \cite{Kim})  %Exercise 21
  Suppose a survey with practicing Medicinae Doctors (MDs) showed about 43\% have a solo
  practice and the remainder 57\% have a partnership, association, are
  employed with HMO or government, etc. Upon reading this survey
  report, a  researcher was curious about the proportion of veterinary physician
  who have a solo practice. She has randomly selected 500 veterinary physician
  listed in a directory and mailed a 
  questionnaire to them. By the end of the month she had
  received 223 responses. The sample proportion of a solo practice
  based on these responses was $\hat{p} = 0.32$. Is the proportion of
  a solo practice among veterinarian physicians different from that among MDs? 
  \begin{enumerate}
  \item State the hypotheses.
  \item Test the hypothesis at the significance level $\alpha = 0.05$.
  \end{enumerate}

\end{problem}

\begin{problem}
  In a random sample of $11$ race horses in a Physical Condition  Test
  the strength of the lateral digital extensor muscle was measured. 
The following values in Kg were got from the sample  
\begin{center}
58, 62, 64, 67, 69, 70, 72, 73, 73, 75, 80 
\end{center}
Assuming that the muscle strength is normally distributed, test whether the population mean is different from $65$
with a significance $\alpha=0.05$. Calculate the value of the test
statistics, the acceptance interval and draw your conclusions.  
\end{problem}
%%%%
\begin{problem}
  A study is being developed about the percentage of wild cats
  infected by toxoplasma (toxoplasmosis). It is known that the percentage of infected cats in Europe is 25\%. A random sample of 125 wild cats has been selected to perform the study. In this sample, a blood analysis has concluded that 35 cats have suffered from this disease.
What conclusion can be drawn from this study with respect to the
percentage of infected cats in Spain and in Europe?  Before answering set the adequate hypothesis testing with a significance of $\alpha=0.05$ and calculate the p--value. 
\end{problem}

\begin{problem}
  We are interested in the height of Arabian horses fed with an
  experimental diet. This horse breed has an average height of
  160\,cm. With the objective of assessing whether the horses get the
  same average height, we have selected 15 horses fed with this new
  type of diet and the mean and standard deviation of the sample were
  162.5\,cm and 5\,cm respectively. Assume that the horse height is
  normally distributed. Can you conclude that the mean height of the horses with this diet is higher than 160\,cm? Before answering, do the hypothesis testing with a significance of $\alpha=0.05$, calculate the acceptance interval and draw your conclusions. 
\end{problem}

\begin{problem}
  In a sample of 1500 dogs from a neighbour of a city, 125 blood test were positive about macrocytic anemia Do these data provide enough evidence that the proportion of dogs with this disease is larger than 6\%? Before answering this question, explain the null and alternative hypothesis and perform the test with a significance level $\alpha=0.05$ and calculate the p-value of this test. 
\end{problem}

\begin{problem}
  A group of veterinarians is trying to determine whether the chloride
  level in the water in a agricultural area with a large number of
  pork farms is adequate. The ideal level is 325 units. A sample of
  water of 150 taps coming from  random selected farms was collected
  by the team.
The mean and the standard deviation is 332 and 52,
respectively. Do the
veterinarian group state whether the chloride level is adequate or
not? 
Explain your reasons by means of a hypothesis testing. 
\end{problem}
