
\section{Exercises}
\label{ch4Exercises}
\begin{problem} % (From \cite{Kim}) % Example 7.2.1
Suppose $X$ is a random variable representing the amount of organic
sulfur contained in $500\,\textrm{mg}$ methyl sulfonyl methane (MSM)
tablets. Organic sulfur plays an important role in the maintenance of
joint cartilage. The formula for MSM requires that each tablet should
contain $85\,\textrm{mg}$ of organic sulfur. To assess how well the
requirement is being followed,  24 MSM tablets were randomly
selected.
Analytic results show that on the average the tablets contain about
$80.5\,\textrm{mg}$ of organic sulfur.
If, based on experience, the amount of organic sulfur found in MSM
tablets is normally distributed with $\sigma = 14.2 \,\textrm{mg}$,
 construct a 95\%--confidence interval of the  population mean $\mu$. \footfullcite{kim2008biostatistics}
\end{problem}



\begin{problem} %(From \cite{Kim}) %problem 6 from chapter 7 
 It is reasonable to assume that the level of triglycerides
 (milligrams per decaliter) is normally distributed. A previous study
 indicates that the variance $\sigma^2$ among male subjects is
 $86.4\,\textrm{mg}^2/\textrm{dL}^2$. We want to use the sample mean of a random sample to estimate
 the population mean of
the triglyceride level and want to be able to assert with probability
0.85 that our error will be no more than (at most) $2.75\,\textrm{mg/dL}$. How
large a sample will we need? \footnote{Ibidem}
\end{problem}


\begin{problem}
  An experiment has been designed in order to estimate the number of
  heartbeat per minute in 5-year-old dogs. The experiment was done
  with 49 dogs randomly selected from a public register and their
  pulses were measured. It was found that the averaged number of
  heartbeat per minute was 90. If the variance of number of beat per minute is $\sigma^2 = 100$, what is the 95\% confidence interval of the mean of the number of beats per minute.
\end{problem}


\begin{problem}
  Gas analysis of arterial blood in a sample of 15 lab rats is
  measured using
  oxinometry. The sample provides
  the following values of the arterial oxygen tension PaO$_2$ for standing gas  
  \begin{center}
    \begin{tabular}{*{15}{c}}
   75, &80, &84, & 74, & 84, &78, & 89, & 72, & 83, & 76,& 75,& 87,&
   78, & 79, & 88  
  \end{tabular}

  \end{center}


Calculate a 95\% confidence interval of the mean of the population if
we can assume that  values of the oxygen tension is normally
distributed.  
\end{problem}

\begin{problem}
  As a part of a study of the queue time in a vet hospital, it was
  reported that a sample of
  100 patients were at the waiting room an averaged time of 23
  minutes. The sample standard deviation was 10 minutes. Calculate a
  90\% confidence interval of the mean waiting time of a patient at
  the vet clinic and interpret the result. 

\end{problem}

\begin{problem}
  A sample of 25 ten year-old male gorillas provided a mean weight and a standard deviation of 36.5\,kg and 5\,kg, respectively. Find a 90\% confidence interval of the mean weight of male gorillas of the population and give an interpretation of that interval.

\end{problem}

\begin{problem}
  The following values are bilirubin concentrations of a sample of 20
  dogs which suffer from hepatitis: 
  \begin{center}
    \begin{tabular}{*{10}{c}}    
20, & 5, & 14, & 8, & 21, & 3, & 12, & 7, & 15, & 2, \\ 
26,&6,&23,&4,&22,&9,&15,&7,&19,&2 
  \end{tabular}
  \end{center}
  
Assuming that values of bilirubin concentration is normally
distributed. Construct a 95\% confidence interval of the mean
bilirubin concentration for dogs suffering from hepatitis. According
to all the studies bilirubin concentration is normally distributed.
\end{problem}
\begin{problem}% (From \cite{Rosner})
  A study is conducted to test the hypothesis that people with glaucoma
  have higher--than--average blood pressure. The study includes 200
  people  with glaucoma whose mean SBP is $140\,\textrm{mmHg}$ with a
  standard deviation of $25\,\textrm{mmHg}$.
  \begin{enumerate}
  \item Construct a 95\%--confidence interval for the true mean SBP
    among people with glaucoma.
  \item If the average SBP for people of comparable age is
    $130\,\textrm{mmHg}$, is there an association between glaucoma
    and blood pressure?\footfullcite{rosner2015fundamentals}
  \end{enumerate}
\end{problem}
\begin{problem}
  We assume that the length  of the Petal for the iris--setosa is
  normally distributed. If the length of 20 flower is the following:
\begin{center}
   \begin{tabular}{*{10}{l}}
    1.4, & 1.4, & 1.3, & 1.5, & 1.4, & 1.7, & 1.4, & 1.5, & 1.4, &
    1.5, \\
 1.5, & 1.6, & 1.4, & 1.1, & 1.2, & 1.5, & 1.3, & 1.4, & 1.7, & 1.5
  \end{tabular}
\end{center}
Find a 95\%--confidence interval for the mean $\mu$ of the petal
length.
\end{problem}
\begin{problem} % Problem 8
  Cardiologists want to estimate the average duration of chest pain experienced by AMI (acute myocardial infarction) patients. Suppose that the duration is normally distributed with variance $\sigma^2 = 424$. Chest pain data were collected from 24 AMI patients who have been admitted to a coronary care unit. With what probability can you assert that the maximum error of estimate will be no greater than $10\,\textrm{min}$?
\end{problem}



% \begin{problem} % (From \cite{Kim}) %Problem 18
%   Homocysteine is a by--product of protein processing, which is known
%   to be one of the serious artery clogging villains. Patients can
%   lower homocysteine levels by taking vitamins, such as folic acid,
%   vitamins B--6 and B--12. Doctors took 29 patients and measured their
%   daily intake of folic acid, which is assumed to be normally
%   distributed. From the measurements they obtained, the sample
%   standard deviation $S = 34\,\textrm{micrograms}$. Find a 90\%
%   confidence interval for the population variance $\sigma^2$. \footfullcite{kim2008biostatistics}
% \end{problem}



\begin{problem} %(From \cite{Rosner})
Suppose a clinical trial is conducted to test the efficacy of a new
drug, spectnomycin, for treating gonorrhea in females. Forty--six
patients are given a 4--g daily dose of the drug and are seen a week
later, at which time 6 of the patients still have gonorrhea. What is a
95\%--confidence interval for $p$ the probability of a failure with
the drug?\footfullcite{rosner2015fundamentals}

\end{problem}

\begin{problem} %(From \cite{Kim}) %%Problem 12 
  A university clinic offers a flu vaccine each year. The flu vaccine
  does not protect individuals from being infected by the flu
  virus. It only reduces the probability of infection. Of 375
  individuals who were given a flu vaccine, 64 had the flu during the
  last flu season. Construct a 90\% confidence interval for the
  proportion of the people who will not get the flu after receiving a
  flu shot.\footfullcite{kim2008biostatistics}

\end{problem}
